Modi normali di oscillazione del Sole (Presentazione)

### 2017-02-08 inversion/variational.tex
inversion/rotation init

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% importa pacchetti
\usepackage{usepkg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Funzioni generali
\usepackage{functions}
%http://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include
\usepackage{sources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Funzioni per questo file main
\usepackage{mathOp}
\usepackage{LocalF}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Modi normali di oscillazione del Sole (Presentazione)}

% A subtitle is optional and this may be deleted
\subtitle{Struttura interna e modi di oscillazione}

%\author{F.~Author\inst{1} \and S.~Another\inst{2}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

%\institute[Universities of Somewhere and Elsewhere] % (optional, but mostly needed)
%{
% \inst{1}
% Department of Computer Science\\
%  University of Somewhere
%  \and
%  \inst{2}%
%  Department of Theoretical Philosophy\\
%  University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date{Tesina 23 Giugno, \today}
% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\subject{Eliosismologia}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.

\section{Importanza studio oscillazioni stellari}

\subsection{Osservabili stellari}

@@

{ % all template changes are local to this group.
    \setbeamertemplate{navigation symbols}{}
    \begin{frame}[plain]{Diagramma di \hr{}}
        \begin{tikzpicture}[remember picture,overlay]
            \node[at=(current page.center)] {
                %\includegraphics[width=\paperwidth]{yourimage}
            };
        \end{tikzpicture}
     \end{frame}
}

\againframe<2>{noinside}

\subsection{Argomenti trattai nella tesina}

\begin{frame}{Eliosismologia}{}
\begin{block}{Oscillazioni dei 5-minuti}
Modi discreti Onde acustiche Cavit\'a risonanti
\end{block}

\begin{block}{Descrizione equazioni di base modello solare}
Importanza misure eliosismologiche di $Y_{ph}$, $d_{cz}$. Diffusione elementi. Dettagli equazione di stato.
\end{block}

\begin{block}{Oscillazoni lineari adiabatiche}
Perturbazioni dello stato di equilibrio. Equazioni delle oscillazioni: soluzioni per determinate frequenze: modi discreti. Soluzioni approssimate.
\end{block}

\begin{block}{Tecniche di inversione}
Informazioni sulla velocit\'a del suono e abbondanza di elio nella zona convettiva: tecniche di inversione usando soluzioni analitiche approssimate.
Inversione non asintotica, linerizzazione delle correzioni attorno ad un modello solare. Correzioni struttura idrostatica e composizione. Vincoli al modello solare.
\end{block}

\subsection{Elisismologia}

\begin{frame}{Pulsazioni stellari}{Modi Normali}
\begin{columns}

\begin{column}{0.5\textwidth}  %%<--- here
    \begin{center}
     %\includegraphics[width=0.5\textwidth]{image1}
     \end{center}
\end{column}

\begin{column}{0.5\textwidth}
\onslide<1-> \begin{block}{Stelle pulsanti}
Onde stazionarie: Pulsazione radiale/non radiale: .

\onslide<2-> meccanismo di eccitazione: solar-like pulsator, Cefeidi.

\onslide<3-> Modo fondamentale $\Pi\approx\tau_{dyn}=\sqrt{\frac{R^3}{GM}}\propto\overline{\rho}\expy{-\frac{1}{2}}$.

\onslide<4-> Modi di oscillazione\onslide<5-> - informazioni sull'interno stellare

\onslide<5-> Elio-sismologia: Modi $\Leftrightarrow$ Modelli solari

\onslide<5-> Astero-sismologia: Modi $\Leftrightarrow$ Spazio parametri modello stellare

\end{block}

\end{column}

\end{columns}
\end{frame}

\section{Oscillazioni solari}

\subsection{Problema osservativo}

\begin{frame}{Fenomeni periodici sulla superficie solare}{Oscillazioni dei 5 minuti}
Oscillazioni nella fotosfera:

Effetto doppler, Variazioni intensit\'a
\pause
\cite{lei62velocity}: righe di ??, 296 s, dimensioni fisiche osservazion ?? 
\pause
caratteristiche oscillazione: ampiezza, frequenze

\pause
Intensit\'a

\subsection{Oscillazioni lineari adiabatiche}

\begin{frame}{Onde in un gas}

\begin{block}{Oscillazioni adiabatiche}

\end{block}

\begin{frame}{Modi normali}{Modello di Ulrich}
Frequenze discrete \pause Distribuzione diagramma $k_h-\omega$.

\pause
Spettro acustic: a basse frequenze non c'\'e propagazione di fase.
(propagazione riflessione densit\'a)
\pause

Interferenza costruttiva

\begin{frame}{Oscillazioni lineari adiabatiche}{Equazione del moto perturbato}
\begin{equation}
\rho\TDof{t}\vec{v}=\rho(\PDof{t}+\scap{v}{\nabla})\vec{v}=-\nabla P+\rho\vec{g}
\end{equation}

% Placing a * after \section means it will not show in the
% outline or table of contents.
\section*{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}

  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}

% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{For Further Reading}

  \begin{thebibliography}{10}

  \beamertemplatebookbibitems
  % Start with overview books.

  \bibitem{Author1990}
    A.~Author.
    \newblock {\em Handbook of Everything}.
    \newblock Some Press, 1990.

  \beamertemplatearticlebibitems
  % Followed by interesting articles. Keep the list short.

  \bibitem{Someone2000}
    S.~Someone.
    \newblock On this and that.
    \newblock {\em Journal of This and That}, 2(1):50--100,
    2000.
  \end{thebibliography}
\end{frame}

>>>>

\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Variational}

\subsection{sub-variational}

@@
